On the power of oritatami cotranscriptional folding with unary bead sequence\thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779 and JST Program to Disseminate Tenure Tracking System No.~6F36 granted to S.~Z.~F. and S.~S.}

### 2018-12-05 tt_theorem.tex

Now, we assume $S[i+2] = t_a$.
%All $S[i+3..j]$ do not contain $t_a$; otherwise $S[i+4..j+1]$ contain $\blacksquare$.
%Therefore, $S[i+2] = t_a$.
According to Lemma~\ref{TTT_tunnelC_lemma}, on statement 1, 2, $\#bc(C_{i-2}) > \#bc(C_{i+2})$ and if $i \leq j - 3$, $\#bc(C_{i+2}) \geq \#bc(C_{j})$.
Thus, binding capability of the conformation decrease per a subsequence $bt_a$ unless $w[i]$ does not consumes any bond.
If $w[i]$ does not consumes any bond and $S[i] = t_a$, that is, $S[i-1..i+2] = bt_abt_a$, then $\#bc(C_{i-3}) - 2 \geq \#bc(C_{i+2})$.
In this case, two subsequences of $bt_a$ collaborate decreasing binding capability but eventually, two subsequences decrease two bond.
That is, one subsequence decrease binding capability.

Hence, if $S[i..j]$ contain n's subsequences of $bt$, $\#bc(C_{i-2}) - n \geq \#bc(C_{j})$
\qed

>>>>

%All $S[i+3..j]$ do not contain $t_a$; otherwise $S[i+4..j+1]$ contain $\blacksquare$.
%Therefore, $S[i+2] = t_a$.
Now, we assume $S[i+2] = t_a$.
Then, we have to make sure that one troll is not double-counted.
If $w[i]$ forms a bond, Lemmas~\ref{TTT_exit} and \ref{TTT_tunnelC_lemma} imply that binding capability decreases through this tunnel.

Assume $w[i]$ forms no bond.
If $S[i] \in \{t_s, t_o\}$, Lemmas~\ref{TTT_exit} and \ref{TTT_tunnelC_lemma} imply $\#bc(C_{i-2}) > \#bc(C_{i+2})$.
Observe that the bead $w[i-1]$ is at the entrance of the previous tunnel or inside.
It is when a bead is stabilized at the entrance of a tunnel that the troll of the tunnel decreases binding capability.
Thus, the inequality does not rely on the troll of previous tunnel.
If $S[i] = t_a$, Lemma~\ref{TTT_tunnelC_lemma} implies $\#bc(C_{i-3}) - 2 \geq \#bc(C_{i+2})$.
The previous tunnel must be indeed a tunnel section of type A (see Fig.~\ref{TTT_tunnelC_enter_usingBond}).
That is, this inequality involves two tunnels but its difference 2 enables us to consider that binding capability decreases by 1 through this tunnel. \qed
%According to Lemma~\ref{TTT_tunnelC_lemma}, on Statement 1, 2, $\#bc(C_{i-2}) > \#bc(C_{i+2})$ and if $i \leq j - 3$, $\#bc(C_{i+2}) \geq \#bc(C_{j})$.
%Thus, binding capability of the conformation decrease per a subsequence $bt_a$ unless $w[i]$ does not consumes any bond.
%If $w[i]$ does not consumes any bond and $S[i] = t_a$, that is, $S[i-1..i+2] = bt_abt_a$, then $\#bc(C_{i-3}) - 2 \geq \#bc(C_{i+2})$.
%In this case, two subsequences of $bt_a$ collaborate decreasing binding capability but eventually, two subsequences decrease two bond.
%That is, one subsequence decrease binding capability.
